Binning Strategies and Related Loss for Large Data

### 2015-12-15 versionForJCGS/PaperJCGS.Rnw
Replace Database connect with more stable pitching.Rdata read-in

# connect <- dbConnect(dbDriver("MySQL"), host="mysql2.stat.iastate.edu", 
#                      port=3306, user="dbaccess", dbname="baseball")
# pitch <- new("dataDB", co=connect, table="Pitching")
# 
# d1 <- dbData(pitch, vars=c( "G", "SO")) # Games, Strike Outs
# 
# xtd.data <- function(x) {
# # replicate each line as often as given by the last entry
#   k <- dim(x)[2]
# 
#   res <- data.frame(sapply(1:(k-1), function(var) {
#   		return(rep(x[,var], x[,k]))
# 		}
# 	))
# 	names(res) <- names(x)[1:(k-1)]
# 	return(res)
# }
# d1.ext <- xtd.data(d1)
# dbDisconnect(connect)
# save(d1, d1.ext, file="pitching.Rdata")
load("pitching.Rdata")
@

@@

<<BaseballBinningExamplePrep, echo=FALSE, eval=TRUE, include=FALSE, cache=TRUE>>=
connect <- dbConnect(dbDriver("MySQL"), host="mysql2.stat.iastate.edu", 
                     port=3306, user="dbaccess", dbname="baseball")
pitchdat <- dbGetQuery(connect,  sprintf("select G, SO from Pitching"))
dbDisconnect(connect)

>>>>

# connect <- dbConnect(dbDriver("MySQL"), host="mysql2.stat.iastate.edu", 
#                      port=3306, user="dbaccess", dbname="baseball")
# pitch <- new("dataDB", co=connect, table="Pitching")
# 
# d1 <- dbData(pitch, vars=c( "G", "SO")) # Games, Strike Outs
# 
# xtd.data <- function(x) {
# # replicate each line as often as given by the last entry
#   k <- dim(x)[2]
# 
#   res <- data.frame(sapply(1:(k-1), function(var) {
#   		return(rep(x[,var], x[,k]))
# 		}
# 	))
# 	names(res) <- names(x)[1:(k-1)]
# 	return(res)
# }
# d1.ext <- xtd.data(d1)
# dbDisconnect(connect)
# pitchdat <- d1.ext
# save(d1, d1.ext,pitchdat, file="pitching.Rdata")
load("pitching.Rdata")
@

@@

<<BaseballBinningExamplePrep, echo=FALSE, eval=TRUE, include=FALSE, cache=TRUE>>=
# connect <- dbConnect(dbDriver("MySQL"), host="mysql2.stat.iastate.edu", 
#                      port=3306, user="dbaccess", dbname="baseball")
# pitchdat <- dbGetQuery(connect,  sprintf("select G, SO from Pitching"))
# dbDisconnect(connect)
